General Procedure

### 2018-07-17 statement.tex
jetzt steht da nicht mehr Mara..... Ach und miriam geht jetzt pennen

\documentclass{article}

@@

\section{Miriam}
My part of the practical part was mostly the RapidMiner part. I did the clustering and decision tree  mining with help of this tool. I evaluated the outcome and adapted the system. Also I gave input about the requirements of the testdata generator, especially the person vector. In the second step, together with Timo, we built the presentation. We merged the different parts and prepared the presentation. In the last step I firstly wrote down my own results and together with Timo joined all the different parts, corrected with Timo the resulting paper and we made the fine tuning of it at the end.

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}

@@

\section{Miriam}
My part of the practical part, the beginning of the practicum, was mostly the RapidMiner. I did the clustering and decision tree  mining with help of this tool. I evaluated the outcome and adapted the system, such that I tried different configurations and all sets generated. Also I gave input about the requirements of the testdata generator, especially the person vector. In the second step, together with Timo, we built the presentation. We merged the different parts and prepared the presentation. In the last step I firstly wrote down my own results and together with Timo joined all the different parts, corrected with Timo the resulting paper and we made the fine tuning of it at the end.
